---
output: 
  html_document:
    keep_md: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mycapstone

<!-- badges: start -->
<!-- badges: end -->

The goal of mycapstone is to analyze the earthquake data that were collected and 
archived by NOAA and that can be found at 
<https://www.ngdc.noaa.gov/hazard/strong.shtml>.

## Installation

You can install the released version of mycapstone from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mycapstone")
```

## Example_clean

This is a basic example which shows you how to clean your data:

```{r example_clean}
library(mycapstone)
## basic example code
data <- utils::read.delim("earthquakes.tsv")
data <- eq_clean_data(data)
data <- eq_location_clean(data)
```

## Example_visualize

This is a basic example which shows you how to visualize your data:

```{r example_visual}
library(mycapstone)
## basic example code
data <- utils::read.delim("earthquakes.tsv")
data <- eq_clean_data(data)
data <- eq_location_clean(data)
data <- dplyr::filter(data, Country == "TURKEY")
geom_timeline_label(data,7.5)
```

## Example_map

This is a basic example which shows you how to create an interactive map from your data:

```{r example_map}
library(mycapstone)
## basic example code
data <- utils::read.delim("earthquakes.tsv")
data <- eq_clean_data(data)
data <- eq_location_clean(data)
data <- dplyr::filter(data, Country == "TURKEY")
data <- dplyr::mutate(data, popup_text = eq_create_label(data))
eq_map(data, "popup_text")
```
